### 2013-05-23 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding solver comparison outputs for mcsa

For the ILUT, SPAINV, and SPAINV-ILUT preconditioning strategies the
reduced domain approximation will be applied to reduce the density of
the composite linear operator to more manageable levels. For each
preconditioner, the parameters that achieved the best quality metric
results from the previous analysis were used with the reduced domain
threshold was set to \sn{1}{-10} in order to eliminate any exceedingly
small values from the matrix (generally this is simply removing
non-zero elements within the floating point tolerance of zero). The
reduced domain fill level was then varied, starting with the largest
non-zero entries per row value observed for each of the
preconditioning types in order to assess its effects relative to the
case where no reduced domain approximation was applied.

>>>>

For the ILUT, SPAINV, and SPAINV-ILUT preconditioning strategies the
reduced domain approximation will be applied to reduce the density of
the composite linear operator to more manageable levels. For each
preconditioner, the parameters that achieved the best quality metric
results from the previous analysis were used with ILUT parameters of a
fill level of 5.0 and a drop tolerance of \sn{1}{-5}, SPAINV
parameters of a sparsity level of 4 and a threshold of 0.1 and
SPAINV-ILUT with ILUT parameters of a fill level of 4.0 and a drop
tolerance of \sn{1}{-5} and SPAINV parameters of a sparsity level of 1
and a threshold of 1.0. The reduced domain threshold was set to
\sn{1}{-10} in order to eliminate any exceedingly small values from
the matrix (generally this is simply removing non-zero elements within
the floating point tolerance of zero). The reduced domain fill level
was then varied, starting with the largest non-zero entries per row
value observed for each of the preconditioning types in order to
assess its effects relative to the case where no reduced domain
approximation was applied.
